\fontsize{14}{14}Bachelor Thesis \\ in \\Allgemeine Informatik \fontsize{22}{22}\textbf{Transhumanism}\\ \fontsize{18}{18} The New Human

### 2014-01-15 draft.tex
Some more changes

      \end{par}
      \begin{par}
        Genetic Engineering is being actively today.
        Today the biggest goal of it is therapeutic applications. 
        There are many genetic diseases and we do not understand them all.
        However once we truly understand our genome it is very possible that we, as a human race, can evolve ourselves.
      \end{par}
      \begin{par}
        This self evolution could lead to brains that are more performant, have a higher memory capacity and might be less prone to diseases.
        A higher athletic condition is also possible by activating or substituting some genes at specific conditions.
      \end{par}
  \section{To Resume}
    \being{par}
      Transhumanism incorporates our current technical advancement and tries to apply it to our own species. 
      Imagining what is possible today and what could be tomorrow.
      This process of trying to make sense of what does not exist yet is fundamental in how we approach science as it allows us to work towards a goal and thus get progress.

@@

\chapter{From the Brain to the Singularity}
  \section{The Superintelligence}
    \subsection{From the Brain to the Computer to the Superbrain}
      \begin{par}

        Explain here how advances in computer intelligence will soon get to critical levels, leading to an intelligence explosion.

      \end{par}
    \subsection{Powering and Nurturing the Computer}
      \begin{par}

>>>>

      \end{par}
      \begin{par}
        Genetic Engineering is being actively today.
        Today the biggest goal of it is therapeutic applications. 
        There are many genetic diseases and we do not understand them all.
        However once we truly understand our genome it is very possible that we, as a human race, can evolve ourselves.
      \end{par}
      \begin{par}
        This self evolution could lead to brains that are more performant, have a higher memory capacity and might be less prone to diseases.
        A higher athletic condition is also possible by activating or substituting some genes at specific conditions.
      \end{par}
  \section{To Resume}
    \begin{par}
      Transhumanism incorporates our current technical advancement and tries to apply it to our own species. 
      Imagining what is possible today and what could be tomorrow.
      This process of trying to make sense of what does not exist yet is fundamental in how we approach science as it allows us to work towards a goal and thus get progress.

@@

\chapter{From the Brain to the Singularity}
  \section{The Superintelligence}
    \subsection{From the Brain to the Computer to the Superbrain}
      \begin{par}
        Moore's law is an often cited observation made in the 60' about the progress of Computer Power. 
        More specifically, Moore stipulated that the number of transistors on integrated circuits doubles approximately every two years. 
        It can be shown that this observation holds true since it has been brought forward.
        This has several implications for future forecasts. 
        One can imagine that through ever progressing technical knowledge a critical amount of calculations per second can be achieved.
        This critical amount would be the equivalent of the human brain.
        We are after all limited through the size and amount of neurons that our brain is made out of.
        This now intelligent Computer could himself design an even more intelligent design or programm of himself.
        Thus, given enough time and energy the intelligence evolves into a superintelligence.
        This process is called the technological singularity due to the unknown factor of what will happen to humankind.
      \end{par}
      \begin{par}
        However there are several hurdles to what will make this intelligence work.
      \end{par}
      \subsubsection{The Program}
        A human, or several, will have to write the program. 
        Which means that it will inherently describe features of humankind.
        This can already be noted today with what is called \emph{Biomimicry}: Humans look at nature and try to replicate it.
        However, many problems arise with this. 
        For one, as Humans we have flaws and these flaws could be very well exacerbated by applying it to a higher machine.
        The problem is also that the same way Chimps cannot understand what we say or do, a superintelligent Computer might be useless to us.
      \subsubsection{The Infrastructure}
        Power today is an important resource, and with the rise of ever faster Computers, this demand for power will rise even more.
        The fastest computer as of today, the Tianhe-2 uses about 20 MW of power per hour. 
        When scaled further up, there will have to be progress for it to be sustainable.
    \subsection{Powering and Nurturing the Computer}
      \begin{par}
